Ownership types in theory and practice (in Rust)

### 2023-01-13 paper/paper.tex
Restructured repo

For example, a string literal can be appended to a mutable String.
\begin{lstlisting}
let mut s = String::from("hello");
s.push\_str("hello");
\end{lstlisting}

@@

\begin{lstlisting}
fn main() {
  let s = String::from("hello");
  let r1 = &s;
  let r2 = &s;
  print\_str(r1);
  print\_str(r2);
}
fn print\_str(s: &String) {
  println!("printed from a reference: {}", s);
}
\end{lstlisting}

@@

\begin{lstlisting}
fn main() {
  let mut s = String::from("hello");
  modify\_str(&mut s);
}
fn modify\_str(s: &mut String) {
  s.push\_str(" world");
}
\end{lstlisting}

@@

let r3 = &mut s; // allowed
r3.push\_str(" world");
println!("{}", r3);
\end{lstlisting}

>>>>

For example, a string literal can be appended to a mutable String.
\begin{lstlisting}
let mut s = String::from("hello");
s.push_str("hello");
\end{lstlisting}

@@

\begin{lstlisting}
fn main() {
  let s = String::from("hello");
  let r1 = &s;
  let r2 = &s;
  print_str(r1);
  print_str(r2);
}
fn print_str(s: &String) {
  println!("printed from a reference: {}", s);
}
\end{lstlisting}

@@

\begin{lstlisting}
fn main() {
  let mut s = String::from("hello");
  modify_str(&mut s);
}
fn modify_str(s: &mut String) {
  s.push_str(" world");
}
\end{lstlisting}

@@

let r3 = &mut s; // allowed
r3.push_str(" world");
println!("{}", r3);
\end{lstlisting}
